Efficient evaluation of threshold queries of derived fields in a numerical simulation database

### 2015-01-22 paper.tex
Added copyright notice and grant acknowledgements.

\begin{document}

@@

\section{Acknowledgments}
The authors would like to thank the Turbulence Database Group at Johns Hopkins University as well as three anonymous reviewers for
their insightful comments and suggestions. This work is supported in part by the National Science Foundation
under Grants CDI-II: CMMI 0941530 and OCI-108849 and Johns Hopkins University's Institute for Data Intensive Engineering \& Science.

>>>>

\begin{document}
%\conferenceinfo{EDBT}{'15 Brussels, Belgium}
%\CopyrightYear{2015} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{ISBN 978-3-89318-067-7}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.

@@

\section{Acknowledgments}
The authors would like to thank the Turbulence Database Group at Johns Hopkins University as well as three anonymous reviewers for
their insightful comments and suggestions. This work is supported in part by the National Science Foundation
under Grants CMMI-0941530, ACI-1261715, OCI-1244820 and AST-0939767 and Johns Hopkins University's 
Institute for Data Intensive Engineering \& Science.
